Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-27 paper/paper.tex
undo deleting appendix (1)

\begin{appendix}
\end{appendix}

>>>>

\begin{appendix}
	\section{Ommited results}
	\begin{enumerate}
		 \item The lower bound of $\Omega(\ell)$ for the scenario with at most $(1/3-1/k)$-augmentation
		 \item Costly cascade example (it is easy to present $k^2$ and $k\cdot \sqrt{k}$ (with different approach), and then we can combine these to obtain $k^3$)
		 \item $k$-competitive algorithm for the ring communication pattern
		 \item $O(\ell)$-competitive algorithm for $k=4$ and $k=5$
	\end{enumerate}

\end{appendix}
